
% If you wish to include an abstract, uncomment the lines below
%Abstract text
%\abstract{

\begin{abstract}
%\textbf{Closed loop approach to Human-Robot Handshake}

\vspace{60px}
%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
%%\section{Environment}
The following work is focusing in the Human-Robot hand interaction, specifically in the grasping force of a handshake. The handshake event between human beings is a well known task, it can to enable a communication between participants as a mixture of physical features like: grip force of the hand, velocity approach, duration of the handshake, oscillation frequency and amplitude of the arm. The hypothesis is is that in human hand-shaking force control there is a balance between an intrinsic (open–loop) and extrinsic (closed–loop) contribution. The target of this work is to set up an environment in order to test the hypothesis for the human-robot handshake grip force.
The environment is built using Robotic Operating System (ROS), which is managing messages among: a Pisa/IIT SoftHand and two FSR 400 sensors managed by an Arduino Uno.
The work is splitted in two main experimental parts: calibration and tests. The calibration part is built as an open loop system in which we're interested in understanding the participants grasping force with respect to robot force. 
The hypothesis is to model the human response to the robot grasp as a dynamical system.
A sensorimotor delay is mimicking the reaction time of Central Nervous System (CNS), and varying the contribution of intrinsic and extrinsic force control modify the perceived handshake quality in the user study.
%
%%\\ 
% Abstract text
 \end{abstract}


